Characterization of gaps in directly bonded Si compound optics

### 2014-03-06 AO_bondedSi.tex
updates of figures, etc.

\begin{figure}[htbp]
\centerline{\includegraphics[width=.5\columnwidth]{figs/SiBondParticle.pdf}}
\caption{Schematic of a particle preventing bonding of two Si surfaces\label{figParticle}}
\end{figure}

@@

\section{Silicon-gap-silicon Fabry-P\`{e}rot theory}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/SiBondTentCatFig.pdf}}
\caption{Schematic of a particle preventing bonding of two Si surfaces\label{figParticle}.  There are two conceivable scenarios in which particle contamination can cause gaps in the bond.  \emph{Left-} The particle serves as a mechanical structure hindering the Si-Si bond from zippering up.  The geometry is like a tent-pole.  \emph{Right-} The particle serves as a catalyst for gas formation.  There is evidence that hydrocarbons can serve as catalysts, the especially pernicious particles are ``thermally unstable hydrocarbon contaminants on the surfaces coming from plastic containers or simply from the ambient in a cleanroom.'' \cite{1998AnRMS..28..215G}. }
\end{figure}

@@

\section{Silicon-gap-silicon Fabry-P\`{e}rot theory}
\label{secTheory}
